### 2018-05-15 doc/large_strain.tex
mention GMG in tex
add a note on caching for large strain

@@

>>>>

\section{Geometric multigrid preconditioning}

TODO[DD]: explain how this works with GMG (eulerian mapping on fine level gets restricted onto the coarse levels, the rest works as-is).
Hopefully we can still use some mappings on coarse level to better represent geometric of inclusions (pores).

@@

TODO: question to asnwer -- how much to cache? At least detF ^ {2/3}. Other options is stress and strain at quadrature points.
Run benchmarks and see.
